---
title: "[TITLE GOES HERE]"
author: "Zach Binney"
date: '2023-08-17'
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# [Q2 BIG HEADING HERE]

## Loading Packages and Data

First we need to load the `Batting` data, which comes as part of the `Lahman` package, as well as some other packages to help us with our analysis.

```{r}
#Load the tidyverse package and `Batting` data
pacman::p_load(tidyverse, Lahman)

data(Batting)
```

Next we want to...[TEXT TELLING READER WHAT THE BELOW CODE IS ABOUT TO DO GOES HERE. SEE THE "MIXING CODE AND TEXT" AND "INCLUDING PLOTS" SECTIONS OF THE RMD_EXAMPLE DOCUMENT WE REVIEWED IN CLASS FOR EXAMPLES.]

```{r exploring_data}

# [CODE TO ACCOMPLISH Q2 GOES HERE. ALSO INCLUDE CODE COMMENTS (THIS GREEN TEXT) AS YOU DEEM NECESSARY TO
# EXPLAIN SPECIFICALLY WHAT CERTAIN PARTS OF YOUR CODE ARE DOING.]


```

[TEXT INTERPRETING THE OUTPUT FROM THE CODE ABOVE GOES HERE, IF NEEDED. SEE THE "MIXING CODE AND TEXT" AND "INCLUDING PLOTS" SECTIONS OF THE RMD_EXAMPLE DOCUMENT WE REVIEWED IN CLASS FOR EXAMPLES. HERE IS AN EXAMPLE OF A GOOD OVERALL DESCRIPTION OF A DIFFERENT DATASET CALLED `diamonds`: "The dataset contains data on the cost, weight in carats, color, and other characteristics of 53,940 round cut diamonds. It has a mix of numerical variables (such as `carat` and `price`) and ordered factors (such as `cut` quality and `color`)."]

# [Q3 BIG HEADING HERE. SUGGESTION: Batting Data Analysis]

## [Q4 SUB-HEADING]

[TEXT TELLING READER WHAT THE BELOW CODE IS ABOUT TO DO GOES HERE.]

```{r [CHUNK_TITLE_HERE]}

# [CODE AND COMMENTS (IF NECESSARY) HERE]


```

[TEXT INTERPRETING THE OUTPUT FROM THE CODE ABOVE GOES HERE, IF NEEDED.]

## [Q5 SUB-HEADING]

[TEXT TELLING READER WHAT THE BELOW CODE IS ABOUT TO DO GOES HERE.]

```{r [CHUNK_TITLE_HERE]}

# [CODE AND COMMENTS (IF NECESSARY) HERE]


```

[TEXT INTERPRETING THE OUTPUT FROM THE CODE ABOVE GOES HERE, IF NEEDED.]

## [Q6 SUB-HEADING]

[TEXT TELLING READER WHAT THE BELOW CODE IS ABOUT TO DO GOES HERE.]

```{r [CHUNK_TITLE_HERE]}

# [CODE AND COMMENTS (IF NECESSARY) HERE]


```

[TEXT INTERPRETING THE OUTPUT FROM THE CODE ABOVE GOES HERE, IF NEEDED.]

## [Q7 SUB-HEADING]

[TEXT TELLING READER WHAT THE BELOW CODE IS ABOUT TO DO GOES HERE.]

```{r [CHUNK_TITLE_HERE]}

# [CODE AND COMMENTS (IF NECESSARY) HERE]


```

[TEXT INTERPRETING THE OUTPUT FROM THE CODE ABOVE GOES HERE, IF NEEDED.]
